### 2016-08-05 notions.tex
cheers

\section{Security Notions}
\label{sec:security-notions}
\tsnote{intro text}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.   
In addition to correctness, we establish three notions of privacy for
set-representations. The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\aux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\aux,q)$ on queries~$q$ of its choosing.  At the end of this game, the adversary must output some point in the set represented by~$M$.  In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two. Then the adversary is given $\aux$ and oracle access to $\Qry(M,\aux,q)$, and it must decide which set~$M$ represents.

@@

First, a set~$S$ is chosen according to some
distribution~$\distr{\calS}{}$ over the collection of multisets
$\mathcal{S}$ associated to~$\Pi$, and then
$\Rep(S)$ is run to generate $(M,\aux)$.
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\calS$ and $\aux$~as input; it is
provided an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
computes (and returns) the result of $\Qry(M,\aux,q)$, and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.

@@

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpCorrect{\setprim,\distr{\calS}{},r}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$\mathrm{err}\gets 0$\\
$(M,\aux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\aux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
  the target multiset~$S$ is sampled from~$\calS$ according to distribution~$\distr{\calS}{}$.} 
\label{fig:correctness}
\end{figure}

@@

\subsection{Notions of Privacy}
One can also consider the orthogonal notion of privacy for a set-representation.
%\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
%to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
%If $S$ has high min-entropy (element-wise), then it might still be
%possible to have security here.}\tsnote{I think we will always bump up
%against the (element-wise) min-entropy of the distribution over~$S$,
%at least in the ``one-wayness'' style definition that I had been imagining. }
There are several possible definitions:
\begin{enumerate}
\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
give the attacker $\aux$ and either $M$ or oracle access to $\Qry$. The attacker
succeeds if it can output an element in~$S$. \tsnote{Neither of these seems to capture the Neidermeier et al. attack.  Giving the adversary~$M$ is closest, but our syntax would put the hash function secret keys into~$M$, which the Neidermeier attack doesn't get.}

\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
must determine which. Here the attacker is given $\aux$ but only oracle access to $\Qry$, and
it is disallowed from asking any query $q$ for which $q(S_0) \neq
q(S_1)$. \tsnote{I'm not convinced this is the right restriction.
  This says that security is required \emph{only} for properties that are
  true of both sets.  So a scheme with $M=S$ will be trivially secure
  against set membership queries.  Maybe we restrict from queries~$q$ that are a priori known to have the same value for all sets~$S \in \calS$, or all~$S$ of a given size, etc., as these might be pointless?)}

\tsnote{Is this the right kind of indistinguishability anyway?  This current notion says, in effect, that $S_0$ and $S_1$ are indistinguishable \emph{with respect to the allowed queries} (assuming that $\aux$ doesn't stupidly leak information.)  But why not try to formalize the intution that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented, period?  (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)   That's tricky to define... Also, if you give~$M$ to the adversary, how do you handle the fact that, under our current syntax, $M$~may contain secret keys, etc.?}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}

\begin{figure}[htbp]
\centering
\hfpages{.495}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\aux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\aux)$\\
if $z \in S$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\aux) \getsr \Rep(S)$\\
$z \getsr A(M,\aux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$
}
}
%
{
\hpagess{.485}{.5}
{
\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
$b \getsr \bits$\\
$S_0,S_1 \getsr \distr{\calS}{}$\\
$(M,\aux) \getsr \Rep(S_b)$\\
$b' \getsr A^{\TestOracle}(S_0,S_1,\aux)$\\
if $b' = b$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\aux) \getsr \Rep(S)$\\
$f \getsr A(M,\aux)$\\
$S' \getsr \distr{\calS}{}$\\
if $f(S) \neq f(S')$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$\\

>>>>

\section{Security Notions}
\label{sec:security-notions}
\tsnote{intro text}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.   
In addition to correctness, we establish three notions of privacy for
set-representations. The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\pubaux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\privaux,q)$ on queries~$q$ of its choosing.  At the end of this game, the adversary must output some point in the set represented by~$M$.  In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two. Then the adversary is given $\pubaux$ and oracle access to $\Qry(M,\privaux,q)$, and it must decide which set~$M$ represents.

@@

First, a set~$S$ is chosen according to some
distribution~$\distr{\calS}{}$ over the collection of multisets
$\mathcal{S}$ associated to~$\Pi$, and then
$\Rep(S)$ is run to generate $(M,\pubaux,\privaux)$.
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\calS$ and $\pubaux$~as input; it is
provided an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
computes (and returns) the result of $\Qry(M,\privaux,q)$, and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.

@@

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpCorrect{\setprim,\distr{\calS}{},r}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$\mathrm{err}\gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
  the target multiset~$S$ is sampled from~$\calS$ according to distribution~$\distr{\calS}{}$.} 
\label{fig:correctness}
\end{figure}

@@

\subsection{Notions of Privacy}
One can also consider the orthogonal notion of privacy for a set-representation.
%\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
%to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
%If $S$ has high min-entropy (element-wise), then it might still be
%possible to have security here.}\tsnote{I think we will always bump up
%against the (element-wise) min-entropy of the distribution over~$S$,
%at least in the ``one-wayness'' style definition that I had been imagining. }
There are several possible definitions:
\begin{enumerate}
\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
give the attacker $\pubaux$ and either $M$ or oracle access to $\Qry$. The attacker
succeeds if it can output an element in~$S$. \tsnote{fixed by
  changing syntax.}\tsnote{Neither of these seems to capture the Neidermeier et al. attack.  Giving the adversary~$M$ is closest, but our syntax would put the hash function secret keys into~$M$, which the Neidermeier attack doesn't get.}

\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
must determine which. Here the attacker is given $\pubaux$ but only oracle access to $\Qry$, and
it is disallowed from asking any query $q$ for which $q(S_0) \neq
q(S_1)$. \tsnote{I'm not convinced this is the right restriction.
  This says that security is required \emph{only} for properties that are
  true of both sets.  So a scheme with $M=S$ will be trivially secure
  against set membership queries.  Maybe we restrict from queries~$q$ that are a priori known to have the same value for all sets~$S \in \calS$, or all~$S$ of a given size, etc., as these might be pointless?)}

\tsnote{Is this the right kind of indistinguishability anyway?  This current notion says, in effect, that $S_0$ and $S_1$ are indistinguishable \emph{with respect to the allowed queries} (assuming that $\pubaux$ doesn't stupidly leak information.)  But why not try to formalize the intution that a representation~$M$ and the public info~$\pubaux$ tell you nothing (non-trivial) about the set being represented, period?  (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)   That's tricky to define... Also, if you give~$M$ to the adversary, how do you handle the fact that, under our current syntax, $M$~may contain secret keys, etc.?}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}

\begin{figure}[htbp]
\centering
\hfpages{.495}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A(M,\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$
}
}
%
{
\hpagess{.485}{.5}
{
\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
$b \getsr \bits$\\
$S_0,S_1 \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S_b)$\\
$b' \getsr A^{\TestOracle}(S_0,S_1,\pubaux)$\\
if $b' = b$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$f \getsr A(M,\pubaux)$\\
$S' \getsr \distr{\calS}{}$\\
if $f(S) \neq f(S')$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\privaux,q)$\\
Return~$a$\\

### 2016-08-05 syntax.tex
cheers

A Bloom filter with secret hash functions is captured by setting $\privaux=(h_1,h_2,\ldots,h_k)$, and setting $\pubaux=\emptystring$.  Related constructions \tsnote{Name them?} that use a secret key~$K$, but not for hashing, are captured setting $\privaux=K, \pubaux=((h_1, \ldots, h_k)$.

>>>>

A Bloom filter with secret hash functions is captured by setting $\privaux=(h_1,h_2,\ldots,h_k)$, and setting $\pubaux=\emptystring$.  Related constructions \tsnote{Name them?} that use a secret key~$K$, but not for hashing, are captured setting $\privaux=K, \pubaux=(h_1, \ldots, h_k)$.
